\thesistitle

### 2019-06-11 sections/research.tex
Talking about type 2 clones

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}. Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type. In such cases refactoring opportunities could be invalidated. An example of such a case is displayed in figure \ref{fig:type1}.

@@

\subsection{Type 2 clones}
Type 2 clones are structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments \cite{roy2007survey}.

\begin{lstlisting}[caption={Methods that are type 2 clones but functionally completely different.},label={lst:type2clone},language=Java]
public boolean containsOnlyRedCircles(List<Circle> listOfCircles){
	return listOfCircles.stream().allMatch(c -> c.isRed());
}

public Apple getEatableAppleFromBasket(FruitBasket<Apple> appleBasket){
	return appleBasket.getFruitContainer().getAppleByCriterium(a -> a.hasNotYetBeenEaten());
}
\end{lstlisting}

@@

\subsection{Type 1R clones} \label{chap:type1rclones}
We propose an alternative definition of type 1 clones. This definition requires cloned fragments to be not just textually equal, but also functionally equal. Although requiring fragements to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones). We check functional equality of two fragments by validating the equality of the fully qualityfied identifier for referenced types, methods and variables.

>>>>

\subsection{Type 1 clones} \label{chap:type1clones}
Type 1 clones are identical clone fragments except for variations in whitespace and comments \cite{roy2007survey}. This allows for the detection of clones that are the result of copying and pasting existing code, along with other reasons why duplicates might get into a codebase.

Type 1 clones are in most cases implemented as textual equality between code fragments (except for whitespace and comments). Although textually equal, method calls can still refer to different methods, type declarations can still refer to different types and variables can be of a different type. In such cases refactoring opportunities could be invalidated. An example of such a case is displayed in figure \ref{fig:type1}.

@@

\subsection{Type 2 clones}
Type 2 clones are structurally/syntactically identical fragments except for variations in identifiers, literals, types, layout and comments \cite{roy2007survey}. This definition allows for the reasoning about code fragments that were copied and pasted, and then slightly modified. The two methods displayed in listing \ref{lst:type2clone} are type 2 clones of each other.

\begin{lstlisting}[caption={Methods that are type 2 clones but functionally completely different.},label={lst:type2clone},language=Java]
public boolean containsOnlyRedCircles(List<Circle> listOfCircles){
	return listOfCircles.stream().allMatch(Shape::isRed);
}

public Apple getEatableAppleFromBasket(FruitBasket<Apple> appleBasket){
	return appleBasket.getFruitContainer().getAppleByCriterium(Fruit::hasNotYetBeenEaten);
}
\end{lstlisting}

Looking at the example in listing \ref{lst:type2clones}, we see an example of a type 2 clone that poses no harm to the system whatsoever. Both methods are, except for their matching structure, completely different in functionality. They operate on different types, call different methods, return different things, etc. Having such a method flagged as a clone does not provide any useful information.

When looking at refactoring, type 2 clones can be very difficult to refactor. For instance if we have variability in types, the code can describe operations on two completely dissimilar types. Type 2 clones do not differentiate between primitives and objects, which makes the these clones often not so useful for refactoring purposes.

@@

\subsection{Type 1R clones} \label{chap:type1rclones}
We propose an alternative definition of type 1 clones. This definition requires cloned fragments to be not just textually equal, but also functionally equal. Although requiring fragements to be functionally equal, type 1R clones do not allow for change in implementation (like type 4 clones). We check functional equality of two fragments by validating the equality of the fully qualityfied identifier for referenced types, methods and variables. Type 1R clones are always a subset of type 1 clones.
